---
title: "STAT 184: Quarto Lesson 1 Worksheet"
format:
  html:
    code-fold: true
    code-tools: true
    df-print: paged
---

In this worksheet, you’ll focus on important commands used in YAML and learn how to style your Quarto document. Answer the following guiding questions as you follow the tutorial.

Link to tutorial: [Online tutorial](https://quarto.org/docs/get-started/computations/rstudio.html)

# Tutorial

This dataset contains a subset of the fuel economy data from the EPA. Specifically, we use the `mpg` dataset from the **ggplot2** package.

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
```

The plots in @fig-mpg show the relationship between city and highway mileage for 38 popular models of cars.
In @fig-mpg-1 the points are colored by the number of cylinders while in @fig-mpg-2 the points are colored by engine displacement.

```{r}
#| label: fig-mpg
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-subcap:
#|   - "Color by number of cylinders"
#|   - "Color by engine displacement, in liters"
#| layout-ncol: 2
#| column: page

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c(option = "E") +
  theme_minimal()
```
```{r}
#| echo: false

mean_cty <- round(mean(mpg$cty), 2)
mean_hwy <- round(mean(mpg$hwy), 2)
```

The average city mileage of the cars in our data is `{r} mean_cty` and the average highway mileage is `{r} mean_hwy`.

# Quarto Tutorial: Computation – Guiding Questions

1.  The `echo` options allow us to choose if we want to show (“echo”) the source code in the output document. Create the following commands within the execute option in the YAML and describe what they do.

    a\. `echo: true`

    b\. `echo: false`

    c\. `echo: fenced`

2.  Which type of output file can we use for code-folding? HTML

3.  What package do we need to install for code-linking?
